Wettability of Doped Two-Dimensional Materials

### 2017-02-22 writing/paper-Tian-gr-wetting.tex
Modify introduction part

% Created 2017-02-22 Wed 14:18
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
  including: (i) the change of 2D materials surface energy, 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
  monolayer 2D material is typically less than 7 degrees. 
  We then study the role of the surface defects and the influence of 2D material choice.
  \textcolor{cyan}{Our analysis show that the defect density has a great impact on the water contact angle on the doped
  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
  we predict that when the the 2D materials is doped by electrostatic gating, 
  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
  and ensures a wider operational region in 2D-material-based liquid phase devices.}
  \textcolor{magenta}{
  FINAL CONCLUSIONS PLACE HOLDER.
  }

@@

The emergence of two-dimensional (2D) materials has attracted broad
interest in various research fields, inspired by their unique physical
and chemical properties. Recent progress of scalable 2D material
synthesis paves the way for their liquid phase 2D-material-based
applications, for instance functional coating
\cite{Prasai_2012,Rafiee_2010,Kim_2014}, nanotribology devices
\cite{Yin_2014,Tang_2016,Feng_2016}, nanoporous desalination apparatus
\cite{Surwade_2015,Rollings_2016,Jain_2015}, droplet manipulation
\cite{Hern_ndez_2013,Vijayarangamuthu_2015}, etc.  To fully exploit the
physics of the interface between 2D materials and liquid phase, a
comprehensive understanding of the 2D-material-liquid interaction, and in
particular, the wettability, is of great importance.

Wetting on atomically-thin 2D materials has long been a hot but highly
disputed topic
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}.
Accurate description of the intrinsic wettability of 2D materials is
known to be challenging. Recent studies show that the wettability on
graphene \cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014} and
MoS\(_{\text{2}}\) \cite{Kozbial_2015,Chow_2015} is strongly affected by airborne
contaminants. Meanwhile, the contact angle measurement technique which
has been widely to determine the wettability on 2D materials, may also
suffer inaccuracy from contact angle hysteresis caused by local
defects \cite{raj_wettability_2013}.  On the other hand, unlike bulk
materials, the thickness of a 2D material falls within the effective
range of dispersion interactions.  As a result, the dispersion
interaction between the substrate underneath the 2D material and
liquid molecules is not fully screened by the 2D material, giving rise
to the fascinating property known as the ``wetting-translucency''
\cite{rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013}.
Moreover, 2D semimetals (graphene, silecene, germanene, etc.) and 2D
semiconductors (e.g, transition metal dichalcogenides (TMDCs)) possess
significantly lower density of states (DOS) than bulk materials,
making them easier to be doped by the underlying substrates
\cite{Chen_2013,Varchon_2007,Giovannetti_2008} or electrostatic gating
\cite{Das_2008,Perera_2013}. Due to the ubiquity of doping in 2D
materials, it is worth investigating the relationship between the
doping level and wettability. Several recent reports have addressed
the issue of doping-induced tunability of graphene's wettability, from
both atomistic simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}
and experimental demonstrations
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016}.
However, discrepancies exist between individual reports, concerning
the origin and magnitude of the doping-induced wetting
tunability. Moreover, to get a full perspective of such phenomenon,
the gap between the nanoscale simulations and macroscopic experimental
results needs to be filled, and the aforementioned issues of intrinsic
wettability and wetting translucency should also be taken into account.

>>>>

% Created 2017-02-22 Wed 21:46
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
  including: (i) the change of 2D materials surface energy, 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
  monolayer 2D material is typically less than 7 degrees. 
  We then study the role of the surface defects and the influence of 2D material choice.
  \textcolor{cyan}{Our analysis show that the defect density plays a crucial role in the water contact angle on the doped
  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
  we predict that when the the 2D material is doped by electrostatic gating, 
  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
  and ensures a wider operational region in 2D-material-based liquid phase devices.}
  \textcolor{magenta}{
  FINAL CONCLUSIONS PLACE HOLDER.
  }

@@

\section{Introduction}
\label{sec:org30908ab}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} [cite some review papers].

\end{minipage}
}
\end{center}
Recent progress in the scalable production of large-area 2D materials
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} cite review papers

\end{minipage}
}
\end{center}
has paved the way for the applications of functional surfaces and
ultrathin membranes.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} cite review papers

The realization of these technologies essentially requires precise
control over the interactions between liquid and the ultrathin
materials, which motivates fundamental research of their
wettability. An accurate determination of the interfacial tension,
nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) interactions is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOSs) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Very recently,
the doping-induced change in the wettability of graphene has been
observed in the contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. However,
most reports described the doping-dependent wettability with the basic
Young-Lippmann equation (YLE) \cite{Lippmann_1875}, whereas the
interplay between the polar orientation of water molecules at the
interface \cite{Shen_2006} and the electronic structure of the 2D
materials is often ignored. In order to address the discrepancies
among the literature, a more complete theoretical picture that bridges
the gap between different length scales is clearly required.
